Check Coverage

### 2019-10-22 analysis/merge_data.Rmd
Adapt to a mapping framework

fd <- biotime_traits %>% 
  filter(!is.na(plot)) %>%
  group_by(study_id, year, plot) %>%
  filter(n_distinct(id) > 4) %>%
  ungroup() %>%
  filter(study_id == 516) %>%
  group_by(study_id, plot) %>%
  group_map(~get_fd_safe(.x, study = .y$study_id, plot = .y$plot)) %>%
  bind_rows()
```

>>>>

data <- biotime_traits %>% 
  filter(!is.na(plot)) %>%
  group_by(study_id, year, plot) %>%
  filter(n_distinct(id) > 4) %>%
  ungroup() %>%
  filter(study_id == 516)

combs <- cross2(unique(data$study_id), unique(data$plot))

fd <- map_df(combs, ~ get_fd_safe(data = data, study = .x[1], plot = .x[2]))  
```
